---
title: "Draw fractals from root finding iteration in R"
author: "Keren Xu"
date: "04/23/2020"
output:
  rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(furrr)
library(RColorBrewer)
library(cartography)
library(Polychrome)
library(Cairo)
library(wesanderson)
```

# NewtonRaphson   

Use NewtonRaphson root finding methods to draw some fractals for some **Complex functions**.  

# Create function newtonraphson  
```{r}
# ftn is the name of a function that has two output including f(x) and f'(x) 
# x0 is the starting point for the algorithm  
# tol is a good stop condition when |f(x)| <= tol for the algorithm, the default here is 1e-9 
# max.iter is a stop condition for the algorithm when n = max.itr 

newtonraphson <- function(ftn, x0, tol = 1e-9, max.iter) {
  # initialize 
  x <- x0
  fx <- ftn(x)
  iter <- 0
  
  # continue iterating until stopping conditions are met  
  while((abs(fx[1]) > tol) && (iter < max.iter)) {
    x <- x - fx[1]/fx[2]
    fx <- ftn(x)
    iter <- iter + 1
    # cat("At iteration", iter, "value of x is:", x, "\n")
  }
  
  # output depends on the success of the algorithm  
  if (abs(fx[1]) > tol){
    # cat("Algorithm failed to converge\n")
    return(data.frame(x0, root = NA, iter = NA))
  } else {
    # cat("Algorithm converged\n")
    return(data.frame(x0, root = x, iter))
  }
  
}
```

# Draw graph for `x^3-1`  
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
F1 <- function(x){
  return(c(x^3-1, 3*(x^2))) 
}

# create complex numbers 
x <- seq(-1, 1, length.out = 500)
y <- seq(-1, 1, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr
plan(multiprocess)

df <- z %>% future_map_dfr(~newtonraphson(F1,.,1e-9, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE)+ scale_fill_gradientn(colors=brewer.pal(12, "Paired"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("turquoise.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Rushmore1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Royal1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Zissou1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("FantasticFox1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Cavalcanti1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("GrandBudapest1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("IsleofDogs1")) + theme_void() + theme(legend.position = "none")

```

# Draw graph for `x^3-1` - Zoom out
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
# create complex numbers 
x <- seq(-10, 10, length.out = 500)
y <- seq(-10, 10, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr
plan(multiprocess)

df <- z %>% future_map_dfr(~newtonraphson(F1,.,1e-9, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")
```



# Draw graph for `x^3-1` - Zoom in
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
# create complex numbers 
x <- seq(-0.01, 0.01, length.out = 500)
y <- seq(-0.01, 0.01, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr
plan(multiprocess)

df <- z %>% future_map_dfr(~newtonraphson(F1,.,1e-9, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")
```


# Draw graph for `x^3-1` - Move a bit to the left  
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
# create complex numbers 
x <- seq(-2, 0, length.out = 500)
y <- seq(-1, 1, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr
plan(multiprocess)

df <- z %>% future_map_dfr(~newtonraphson(F1,.,1e-9, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")
```


# Draw graph for `x^3-1` - Zoom in  
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
# create complex numbers 
x <- seq(-1, -0.5, length.out = 500)
y <- seq(-0.25, 0.25, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr
plan(multiprocess)

df <- z %>% future_map_dfr(~newtonraphson(F1,.,1e-9, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")
```



# Draw graph for `x^5-1`  
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}  
F2 <- function(x){
  return(c(x^5-1,5*(x^4))) 
}

# create complex numbers   
x <- seq(-5, 5, length.out = 500)
y <- seq(-5, 5, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr  
plan(multiprocess)

df <- z %>% future_map_dfr(~newtonraphson(F2,.,1e-9, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE)+ scale_fill_gradientn(colors=brewer.pal(12, "Paired"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("turquoise.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Rushmore1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Royal1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Zissou1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("FantasticFox1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Cavalcanti1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("GrandBudapest1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("IsleofDogs1")) + theme_void() + theme(legend.position = "none")  
 
```


# Draw graph for `x^3-0.64310316*x-0.35689684`   
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
F3 <- function(x){
  return(c(x^3-0.64310316*x-0.35689684, 3*x^2-0.64310316))
}

x <- seq(-5, 5, length.out = 500)
y <- seq(-5, 5, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr  
plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F3,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE)+ scale_fill_gradientn(colors=brewer.pal(12, "Paired"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("turquoise.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Rushmore1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Royal1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Zissou1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("FantasticFox1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Cavalcanti1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("GrandBudapest1")) + theme_void() + theme(legend.position = "none")


df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("IsleofDogs1")) + theme_void() + theme(legend.position = "none") 
 
```


# Draw graph for `x^3-0.64310316*x-0.35689684`
```{r, fig.height = 4, fig.width = 6, fig.align = "center"}
F3 <- function(x){
  return(c(x^3-0.64310316*x-0.35689684, 3*x^2-0.64310316))
}

x <- seq(-1.5, 1.5, length.out = 500)
y <- seq(-1, 1, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr  
plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F3,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none") 

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")
```

# Draw graph for `x^3-0.64310316*x-0.35689684`
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
F3 <- function(x){
  return(c(x^3-0.64310316*x-0.35689684, 3*x^2-0.64310316))
}

x <- seq(-0.5, 0.5, length.out = 500)
y <- seq(-0.5, 0.5, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr  
plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F3,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2"), na.value = 'black') + theme_void() + theme(legend.position = "none")
```


# Draw graph for `x^3-0.64310316*x-0.35689684`
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
F3 <- function(x){
  return(c(x^3-0.64310316*x-0.35689684, 3*x^2-0.64310316))
}

x <- seq(-0.05, 0.05, length.out = 500)
y <- seq(-0.03, 0.07, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr  
plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F3,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2"), na.value = 'black') + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"), na.value = 'black') + theme_void() + theme(legend.position = "none")
```



# Draw graph for `x^3-0.64310316*x-0.35689684`
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}
F3 <- function(x){
  return(c(x^3-0.64310316*x-0.35689684, 3*x^2-0.64310316))
}

x <- seq(-0.15, 0.15, length.out = 500)
y <- seq(-0.15, 0.15, length.out = 500)
z <- outer(x, 1i*y,'+')

# parallel processing using furrr  
plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F3,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")
```

# Draw graph for `(exp(x)+exp(‑x))/2 - 1`      
```{r, fig.height = 2, fig.width = 8, fig.align = "center"}

F5 <- function(x){
  return(c((exp(x)+exp(‑x))/2 - 1, (exp(x) - exp(-x))/2))
}


x <- seq(-4, 4, length.out = 1000)
y <- seq(2, 4, length.out = 500)
z <- outer(x, 1i*y,'+')

plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F5,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE)+ scale_fill_gradientn(colors=brewer.pal(12, "Paired"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("turquoise.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Rushmore1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Royal1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Zissou1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("FantasticFox1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Cavalcanti1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("GrandBudapest1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("IsleofDogs1")) + theme_void() + theme(legend.position = "none")



```


# Draw graph for `x^8 + 15*x^4 - 16`      
```{r, fig.height = 6, fig.width = 6, fig.align = "center"}

F6 <- function(x){
  return(c(x^8 + 15*x^4 - 16, 8*x^7 + 60*x^3))
}


x <- seq(-5, 5, length.out = 1000)
y <- seq(-5, 5, length.out = 500)
z <- outer(x, 1i*y,'+')   

plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F6,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE)+ scale_fill_gradientn(colors=brewer.pal(12, "Paired"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("turquoise.pal"))+ theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Rushmore1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Royal1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Zissou1")) + theme_void() + theme(legend.position = "none")
  
df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Darjeeling2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("FantasticFox1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Cavalcanti1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("GrandBudapest1")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("IsleofDogs1")) + theme_void() + theme(legend.position = "none")

```



# Draw graph for `sin(x) - 1`  
```{r, fig.height = 6, fig.width = 5, fig.align = "center"}

F7 <- function(x){
  return(c(sin(x) - 1, cos(x)))
}

x <- seq(-4, 1, length.out = 500)
y <- seq(-3, 3, length.out = 500)
z <- outer(x, 1i*y,'+')  


plan(multiprocess)
df <- z %>% future_map_dfr(~newtonraphson(F7,.,1e-3, 40), .progress = TRUE)

df$x <- Re(df$x0)
df$y <- Im(df$x0)

# color by iteration  

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("Moonrise3")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = wes_palette("BottleRocket2")) + theme_void() + theme(legend.position = "none")

df %>% ggplot(aes(x = x, y = y)) + geom_raster(aes(fill = iter), interpolate = TRUE) + scale_fill_gradientn(colors = carto.pal("multi.pal"))+ theme_void() + theme(legend.position = "none")
```


# Secant method  
```{r}
secant <- function(ftn, x0, x1, tol = 1e-9, max.iter) {
  # initialize 
  x_n0 <- x0
  x_n1 <- x1
  ftn_n0 <- ftn(x_n0)
  ftn_n1 <- ftn(x_n1)
  iter <- 0
  
  # continue iterating until stopping conditions are met  
  while((abs(ftn_n1) > tol) && (iter < max.iter)) {
    x_n2 <- x_n1 - ftn_n1*(x_n1 - x_n0)/(ftn_n1 - ftn_n0)
    x_n0 <- x_n1
    ftn_n0 <- ftn(x_n0)
    x_n1 <- x_n2
    ftn_n1 <- ftn(x_n1)
    iter <- iter + 1
    # cat("At iteration", iter, "value of x is:", x_n1, "\n")
  }
  
  return(c(x_n1, iter))
}   

```





